Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-12 document/ms.tex
figures and captions

% Document specific variables.
\newcommand{\rate}{\ensuremath{\Gamma}}
\newcommand{\ratepar}{{\ensuremath{\theta}}}
\newcommand{\ratepars}{{\ensuremath{\bvec{\ratepar}}}}
\newcommand{\obs}[1]{\ensuremath{\hat{#1}}}
\newcommand{\radius}{\ensuremath{R}}
\newcommand{\period}{\ensuremath{T}}
\newcommand{\completeness}{{\ensuremath{P_\mathrm{c}}}}
\newcommand{\transitprob}{{\ensuremath{P_\mathrm{t}}}}
\newcommand{\data}{{\ensuremath{\bvec{x}}}}
\newcommand{\entry}{{\ensuremath{\bvec{w}}}}
\newcommand{\catalog}{{\ensuremath{\bvec{\entry}}}}

@@

@@

We generate synthetic catalogs from two qualitatively different rate
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first model has a smooth occurence surface where both distributions are
smooth broken power laws.
The second is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.

For each catalog, we directly applied the inverse-detection-efficiency
procedure as implemented by \citealt{petigura}\footnote{our implementation
exactly reproduces their results when applied to the published catalog} and
our probabilistic method.

@@

% \begin{figure}[htbp]
% \begin{center}
% \subfigure[one-over-efficiency]{%
% \includegraphics[width=0.45\textwidth]{figures/synthetic-vmax-radius.pdf}
% }
% \subfigure[fully-marginalized forward model]{%
% \includegraphics[width=0.45\textwidth]{figures/synthetic-radius.pdf}
% }
% \end{center}
% \caption{%
% The inferred distribution of exoplanet radii based on a noisy observation of a
% synthetic catalog.
% The red dotted line shows the true distribution function and the black
% histograms are the constraints from the different inference techniques.
% \figlabel{synthetic-radius}}
% \end{figure}

@@

@@

>>>>

% Document specific variables.
\newcommand{\rate}{\ensuremath{\Gamma}}
\newcommand{\ratepar}{{\ensuremath{\theta}}}
\newcommand{\ratepars}{{\ensuremath{\bvec{\ratepar}}}}
\newcommand{\obs}[1]{\ensuremath{\hat{#1}}}
\newcommand{\radius}{\ensuremath{R}}
\newcommand{\period}{\ensuremath{P}}
\newcommand{\completeness}{{\ensuremath{P_\mathrm{c}}}}
\newcommand{\transitprob}{{\ensuremath{P_\mathrm{t}}}}
\newcommand{\data}{{\ensuremath{\bvec{x}}}}
\newcommand{\entry}{{\ensuremath{\bvec{w}}}}
\newcommand{\catalog}{{\ensuremath{\bvec{\entry}}}}

@@

\newcommand{\modela}{\emph{Model A}}
\newcommand{\modelb}{\emph{Model B}}

\newcommand{\gammaearth}{{\ensuremath{\rate_\oplus}}}

@@

We generate synthetic catalogs from two qualitatively different rate
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first model---\modela---has a smooth occurence surface where both
distributions are smooth broken power laws.
The second---\modelb---is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.

For each catalog, we directly apply the inverse-detection-efficiency
procedure as implemented by \citealt{petigura}\footnote{Our implementation
exactly reproduces their results when applied to the published catalog.} and
our probabilistic method.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/smooth/results.pdf}
\end{center}
\caption{%
Inferences about the occurence rate function based on the simulated catalog
\modela.
\emph{Center:} the points with error bars show the exoplanet candidates in the
simulated incomplete catalog, the contours show the survey completeness
function (\citealt{petigura}), and the grayscale shows the median posterior
occurence surface.
\emph{Top and left:} the red dashed line shows the \emph{true} distribution
that was used to generate the catalog, the points with error bars show the
results of the inverse-detection-efficiency procedure, and the histograms are
posterior samples from the marginalized occurence rate as inferred by our
method.
\figlabel{smooth-results}}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/simulation/results.pdf}
\end{center}
\caption{%
The same as \fig{smooth-results} for \modelb.
\dfmtodo{UPDATE THIS FIGURE TO FINAL VERSION}
\figlabel{simulation-results}}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/smooth/rate.pdf}
\end{center}
\caption{%
The extrapolated rate of Earth analogs \gammaearth\ as inferred by the
different techniques.
Applying the method used by \citet{petigura} gives a constraint indicated by
the vertical black line with error bars shown as dashed lines.
The histogram is the MCMC estimate of our posterior constraint on this rate
and the true value is indicated as the thick gray vertical line.
\figlabel{smooth-rate}}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/simulation/rate.pdf}
\end{center}
\caption{%
The same as \fig{smooth-rate} for \modelb.
\dfmtodo{UPDATE THIS FIGURE TO FINAL VERSION}
\figlabel{simulation-rate}}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/results/results.pdf}
\end{center}
\caption{%
The same as \fig{smooth-results} when applied to the observed data from
\citet{petigura}.
\figlabel{real-results}}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/results/rate.pdf}
\end{center}
\caption{%
The same as \fig{smooth-rate} but applied to the catalog from \citet{petigura}.
\figlabel{real-rate}}
\end{figure}
